How explicit is the Explicit Formula?

### 2013-01-05 talk/talk.tex
Can I bootstrap it instead?

\begin{frame}
   $$\Delta_E(X): =\sum_{p\le X}\gamma_E(p).$$

@@

\begin{frame}
 More generally we might consider  weighting functions $p \mapsto g_E(p)$ that have the property that }  \end{frame}

\begin{frame}\vskip20pt
{\Large \vskip40pt
\begin{itemize} \item for all primes $p$, $g_E(p)$ is an {\it odd} function of the value  $a_E(p)$, and \vskip20pt \item the {\it sum\ of\ local\ data}  $$\delta_E(X):=\sum_{p\le X}g_E(p)$$ has---or can be convincingly conjectured to have---a finite  {\it mean}.\end{itemize}}\end{frame}
%\end{document}
\begin{frame}\vskip20pt
{\Large \vskip40pt
Any such  $$p \mapsto  g_E(p)$$ represents a version of a `bias race'.
\vskip20pt
To illustrate specific features of the `Explicit Formula' we focus on three examples of such races for an elliptic curve $E$. }\end{frame}
  %\end{document}
\begin{frame}\vskip20pt
{\Large  \vskip20pt  Form  these 'sums of local data' ---\vskip20pt

>>>>

\begin{frame}
   $$\Delta_E(X): =\sum_{p\le X}\gamma_E(p)$$

{\bf 11a:}
{\bf 37a:}

{\bf 389a:}
{\bf 5077a:}

{\bf 234446a:}
{\bf ????a:}

@@

\begin{frame}
  More generally we might consider  weighting functions $p \mapsto g_E(p)$ that have the property that:

  \begin{itemize} \item for all primes $p$, $g_E(p)$ is an {\it odd} function of the value  $a_E(p)$, and \vskip20pt \item the {\it sum\ of\ local\ data}  $$\delta_E(X):=\sum_{p\le X}g_E(p)$$ has---or can be convincingly conjectured to have---a finite  {\it mean}.
  \end{itemize}

\end{frame}
%\end{document}
\begin{frame}\vskip20pt
{\Large \vskip40pt
Any such  $$p \mapsto  g_E(p)$$ represents a version of a `bias race'.
\vskip20pt
To illustrate specific features of the `Explicit Formula' we focus on three examples of such races for an elliptic curve $E$. }\end{frame}
  %\end{document}
\begin{frame}\vskip20pt
{\Large  \vskip20pt  Form  these 'sums of local data' ---\vskip20pt
